---
title: "Code_Jan_2026"
output: html_document
toc: true
---

## Reproducibility (Stable Code Reference)

This analysis corresponds to the GitHub repository `yangfengstat/np-crisis` at the tagged release `v1.0`.
For a stable link (not a moving branch), cite:

- `https://github.com/yangfengstat/np-crisis/tree/v1.0`
- `https://github.com/yangfengstat/np-crisis/releases/tag/v1.0` (once the GitHub Release is created)

To reproduce this exact version:

```bash
git clone https://github.com/yangfengstat/np-crisis.git
cd np-crisis
git checkout v1.0
```

R package versions are recorded in `renv.lock`; restore them with `renv::restore()`.

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())

##### Library setup #####

library(dplyr)
library(ggplot2)
library(foreach)

required_pkgs <- c(
  "data.table", "doParallel", "e1071", "foreign", "ggpubr", "imputeMissings",
  "nproc", "randomGLM", "readr", "readxl", "rfUtilities", "ROCR", "ROSE",
  "rpart", "tidyr", "zoo"
)
missing_pkgs <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_pkgs) > 0) {
  stop("Missing required packages: ", paste(missing_pkgs, collapse = ", "), call. = FALSE)
}

if (FALSE) {
  requireNamespace("e1071")
  requireNamespace("randomGLM")
  requireNamespace("ROSE")
  requireNamespace("rpart")
}

data_dir <- "data"
output_dir <- "outputs"
output_rds_dir <- file.path(output_dir, "rds")
dir.create(output_rds_dir, recursive = TRUE, showWarnings = FALSE)

use_cached_rds <- TRUE  # if TRUE and cached .rds exist, skips expensive computation

rds_path <- function(filename) {
  file.path(output_rds_dir, filename)
}

save_rds <- function(obj, filename) {
  saveRDS(obj, rds_path(filename))
}

```

### Functions
```{r functions}
source("np-crisis-helper-funcs.R")
```

### Data Import
```{r data import}

Datasets <- c("External - EMP Crises VEA", 
              "External - EMP Crises VEE",
              "External - EMP Crises VELIC", 
              "External - EMP Crises",
              "External - Sudden Stops without GI", 
              "External - Sudden Stops with GI")

Performance <- data.frame(matrix(, nrow = 100, ncol = 59))
# Name variables in Performance
names(Performance)<-c("Data", "year.cutoff", "Model", 
                      "Error.training", "False.training", "Missed.training", 
                      "Error.tuning.mean", "Error.tuning.sd", 
                      "False.tuning.mean", "False.tuning.sd", 
                      "Missed.tuning.mean", "Missed.tuning.sd", 
                      "Error.tuning_out.mean", "Error.tuning_out.sd", 
                      "False.tuning_out.mean", "False.tuning_out.sd", 
                      "Missed.tuning_out.mean", "Missed.tuning_out.sd", 
                      "Error.test", "False.test", "Missed.test", 
                      "Error.tuning.threshold.mean", "False.tuning.threshold.mean", "Missed.tuning.threshold.mean", 
                      "Error.tuning.threshold.sd", "False.tuning.threshold.sd", "Missed.tuning.threshold.sd", "Threshold.tuning.mean", 
                      "Error.tuning_out.threshold.mean", "False.tuning_out.threshold.mean", "Missed.tuning_out.threshold.mean", 
                      "Error.tuning_out.threshold.sd", "False.tuning_out.threshold.sd", "Missed.tuning_out.threshold.sd",
                      "Error.training.threshold", "False.training.threshold", "Missed.training.threshold", "Threshold.training", 
                      "Error.test.threshold", "False.test.threshold", "Missed.test.threshold",
                      "Error.test.threshold_tuning", "False.test.threshold_tuning", "Missed.test.threshold_tuning",
                      "AUC.tuning.mean", "AUC.tuning_out.mean", "AUC.training", "AUC.test",
                      "Predictor.1st", "Predictor.2nd", "Predictor.3rd", "Predictor.4th", "Predictor.5th",
                      "Predictor.6th", "Predictor.7th", "Predictor.8th", "Predictor.9th", "Predictor.10th",
                      "Parameters")

Performance$Data <- as.character(Performance$Data)
Performance$Model <- as.character(Performance$Model)

storemodels <- list()

Today <- format(Sys.Date(),"%m_%d_%y")
file_suffix <- paste("_", Today, sep="");
```

### Choice of Variables

```{r choice of variables}
External_database <- "External_database"
Crisis_definition <- "_withSuddenStopGI"
Period_coverage <- "_19802019"
Date_constructed <- "_public_09_18_2019"
forecasting_horizon <- 1
if (forecasting_horizon == 1){
  suffix <- "_forecasting_h1_v12"
}
data <- 6
year.cutoff<- 2007
test_size <- 10
alpha.choice <- seq(0.05, 1, by = 0.05)
ratio <- FALSE
weight <- NULL
res.id <- 0
weight_false <- NULL
model.choice = c("SE", "logistic", "svm", "randomforest", "ada")
method_screening <- "Kfilter"
n.model <- length(model.choice)
```

### Training
```{r training}

filename <- file.path(
  data_dir,
  paste0(External_database, Crisis_definition, Period_coverage, Date_constructed, suffix, ".dta")
)
current <- foreign::read.dta(filename, missing.type = FALSE, convert.underscore = FALSE)
# current <- current[which(current$Year >= 1990),]
current$outcome <- current$SuddenStop_GI
firstvar <- 5
year.start <- min(current$Year)
year.end <- max(current$Year)
Country_Crisis <- aggregate(current[current$Year <= 2007,]$SuddenStop_GI, by=list(Category = current[current$Year <= 2007,]$Country_Name), FUN = sum, na.rm = TRUE)
names(Country_Crisis) <- c('Country_Name', 'Num_Crisis')
Country_withCrisis <- Country_Crisis[Country_Crisis$Num_Crisis>0,]
Country_withCrisis$Optimal_Alpha <- NA

row.id <- 0

if (data == 5){
  prior <- foreign::read.dta(file.path(data_dir, "Prior_SS_08_04_2019_v12.dta"), missing.type = FALSE, convert.underscore = FALSE)
  # 1: the higher, the riskier
  # 0: the lower, the riskier
}else if (data == 6){
  prior <- foreign::read.dta(file.path(data_dir, "Prior_SSGI_08_04_2019_v12.dta"), missing.type = FALSE, convert.underscore = FALSE)
  # 1: the higher, the riskier
  # 0: the lower, the riskier
}

prior <- readxl::read_excel(file.path(data_dir, "External_Variable_Riskiness_SSGI-19802019_SE_h1_22-Sep-2019.xlsx"), sheet = 1)

prior_temp <- prior[which(prior$Year_cutoff==year.cutoff),]

current_working <- current[which(current$Year <= year.cutoff + test_size), ]
###### drop variables for which all observations miss data -----

temp0 <- colSums(!is.na(current_working))
current_working <- current_working[,which(temp0!=0)]

###### drop observations for which all variables miss data -----
temp0 <- rowSums(!is.na(current_working[,c(firstvar:NCOL(current_working)-1)]))
current_working <- current_working[which(temp0!=0),]

###### set training sample and test sample -----
current.training <- current_working[which(current_working$Year <= year.cutoff),]
current.forecasting <- current_working[which(current_working$Year > year.cutoff & current_working$Year <= year.cutoff+ test_size),]
forecasting_row <- NROW(current.forecasting)

######## drop observations with missing outcome -----
current.training <- current.training[!is.na(current.training$outcome),]
current.test <- current.forecasting[!is.na(current.forecasting$outcome),]

####### Median imputation -----
predictor.name <- colnames(current.training[,c(firstvar:(NCOL(current.training)-1))])
training.median <- imputeMissings::compute(current.training[,predictor.name])
trainingSample <- current.training
trainingSample[, predictor.name] <- imputeMissings::impute(trainingSample[, predictor.name], object = training.median)
testSample <- current.test
forecastingSample <- current.forecasting

testSample[, predictor.name] <- imputeMissings::impute(testSample[, predictor.name], object = training.median)
forecastingSample[, predictor.name] <- imputeMissings::impute(forecastingSample[, predictor.name], object = training.median)

training_size <- NROW(trainingSample)

trainingSample.NP <- trainingSample
testSample.NP <- testSample
forecastingSample.NP <- forecastingSample

# npc designs that 0 indicates crisis and 1 indicates non-crisis. Therefore, labels should be exchanged.

trainingSample.NP$outcome <- 1 - trainingSample.NP$outcome
testSample.NP$outcome <- 1 - testSample.NP$outcome
forecastingSample.NP$outcome <- 1 - forecastingSample.NP$outcome

# Neyman-Pearson designs that the higher the value, the safer the observation. Therefore, those with prior value 1 (i.e. the higher the riskier) should be made to the negative value

trainingSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))] <- -trainingSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))]
testSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))] <- -testSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))]
forecastingSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))] <- -forecastingSample.NP[,intersect(predictor.name,names(prior_temp[,which(prior_temp==1)]))]

# remove variable DB_GDP_BIS_FC because it is constant in the training sample
predictor.name <- predictor.name[which(predictor.name != "DB_GDP_BIS_FC")]
smaller_size.choice <- c(seq(10, length(predictor.name), by = 10), length(predictor.name))
df.predictor <- data.frame(size = smaller_size.choice)

nproc.tranining <- list()
nproc.test <- list()

nproc_results_rds <- rds_path("nproc_results.rds")
use_cached_nproc_results <- use_cached_rds && file.exists(nproc_results_rds)

if (use_cached_nproc_results) {
  nproc.results <- readRDS(nproc_results_rds)
} else {
  screen.rank <- NULL
  if (method_screening == "Goffins"){
    data_screening <- list("x" = trainingSample.NP[, predictor.name], "y" = trainingSample.NP$outcome)
    screen.rank <- getGFsize(data_screening, family.type = 1)$rank
  }else if(method_screening == "Kfilter"){
    screen.rank <- k.filter(x = trainingSample.NP[, predictor.name], y =as.factor(trainingSample.NP$outcome), response.type = "categorical")$k.rank
    write.csv(screen.rank, "./outputs/Rank_Kfilter.csv")
  }else if(method_screening == "SIRS"){
    screen.rank <- SIRS(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
  }else if (method_screening == "DC"){
    screen.rank <- DC(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
  }else{
    stop(paste("Unknown method_screening:", method_screening))
  }

  combo <- expand.grid(smaller_size = smaller_size.choice, alpha = alpha.choice, KEEP.OUT.ATTRS = FALSE, stringsAsFactors = FALSE)

  n_cores_requested <- 11L
  n_cores_available <- parallel::detectCores(logical = FALSE)
  if (is.na(n_cores_available)) {
    n_cores_available <- parallel::detectCores(logical = TRUE)
  }
  n_cores <- min(n_cores_requested, n_cores_available, nrow(combo))
  if (is.na(n_cores) || n_cores < 1L) {
    n_cores <- 1L
  }

  cl <- parallel::makeCluster(n_cores)
  doParallel::registerDoParallel(cl)

  nproc.results <- foreach(row_idx = seq_len(nrow(combo)),
                           .combine = rbind,
                           .packages = c("nproc", "e1071", "randomGLM", "ROSE", "rpart"),
                           .export = c("npc.signalextraction", "npc.signalextraction.split", "npc_aux.core",
                                       "predict.signalextraction", "SumErrors.label")) %dopar% {
    alpha <- combo$alpha[row_idx]
    smaller_size <- combo$smaller_size[row_idx]

    predictor.name.smaller <- predictor.name[which(screen.rank <= smaller_size)]

    train_vals <- setNames(rep(NA_real_, n.model), model.choice)
    test_vals <- setNames(rep(NA_real_, n.model), model.choice)

    for (i.model in seq_len(n.model)){

      Performance$Data[res.id] <- Datasets[data]
      Performance$year.cutoff[res.id] <- year.cutoff
      Performance$Model[res.id] <- model.choice[i.model]

      print(c(alpha, Datasets[data], year.cutoff, model.choice[i.model]))

      ##### "Neyman-Pearson::Signal Extraction Model" #####

      if (i.model == 1){
        model.trained <- npc.signalextraction(trainingSample.NP, trainingSample.NP$outcome, predictor.name.smaller, alpha = alpha, delta = 0.1, split = 1, split.ratio = 0.5, n.cores = 1, randseed = 0)
        score.training <- 1-predict.signalextraction(trainingSample.NP, model.trained, predictor.name.smaller)
        score.test <- 1-predict.signalextraction(testSample.NP, model.trained, predictor.name.smaller)
        label.training <- ifelse(score.training > 0.5, 1, 0)
        label.test <- ifelse(score.test > 0.5, 1, 0)
      }else{
        model.trained <- nproc::npc(trainingSample.NP[, predictor.name.smaller], trainingSample.NP$outcome, method = model.choice[i.model], alpha = alpha, delta = 0.1, split = 1, split.ratio = 0.5, n.cores = 1, randSeed = 0)
        pred.training <- predict(model.trained, trainingSample.NP[, predictor.name.smaller])
        pred.test <- predict(model.trained, testSample.NP[, predictor.name.smaller])
        score.training <- 1 - pred.training$pred.score
        score.test <- 1 - pred.test$pred.score
        label.training <- 1 - pred.training$pred.label
        label.test <- 1 - pred.test$pred.label
      }

      names(score.training) <- "Score"
      names(score.test) <- "Score"

      posterior.training <- cbind(trainingSample[,c("Country_Code", "Country_Name", "Year", "SuddenStop_GI")], score.training)
      posterior.test <- cbind(testSample[,c("Country_Code", "Country_Name", "Year", "SuddenStop_GI")], score.test)

      train_vals[[model.choice[i.model]]] <- ifelse(is.na(SumErrors.label(label.training, trainingSample$outcome, weight = NULL)$false), 0, 1-SumErrors.label(label.training, trainingSample$outcome, weight = NULL)$false)
      test_vals[[model.choice[i.model]]] <- ifelse(is.na(SumErrors.label(label.test, testSample$outcome, weight = NULL)$false), 0, 1-SumErrors.label(label.test, testSample$outcome, weight = NULL)$false)
    }

    c(
      missed.crises = alpha,
      screen.size = smaller_size,
      setNames(train_vals, paste0("train_", model.choice)),
      setNames(test_vals, paste0("test_", model.choice))
    )
  }

  parallel::stopCluster(cl)
}

nproc.results <- as.data.frame(nproc.results, stringsAsFactors = FALSE)
if (!use_cached_nproc_results) {
  save_rds(nproc.results, "nproc_results.rds")
}
nproc.tranining.df <- nproc.results[, c("missed.crises", "screen.size", paste0("train_", model.choice))]
names(nproc.tranining.df) <- c("missed.crises", "screen.size", model.choice)

nproc.test.df <- nproc.results[, c("missed.crises", "screen.size", paste0("test_", model.choice))]
names(nproc.test.df) <- c("missed.crises", "screen.size", model.choice)
```

### Calculate AUC
```{r auc}
smaller_size.choice <- c(10,20,30,40,50,60,70,71)
feature_cols <- paste0("features_", smaller_size.choice)
df.auc.test <- as.data.frame(matrix(NA_real_, ncol = length(smaller_size.choice), nrow = n.model))
colnames(df.auc.test) <- feature_cols
df.pauc.test <- as.data.frame(matrix(NA_real_, ncol = length(smaller_size.choice), nrow = n.model))
colnames(df.pauc.test) <- feature_cols
pauc.max.fpr <- 0.25

pauc_np <- function(x, y, max_fpr = 0.25) {
  keep <- is.finite(x) & is.finite(y)
  x <- x[keep]
  y <- y[keep]
  if (length(x) < 2) {
    return(NA_real_)
  }
  id <- order(x)
  x <- x[id]
  y <- y[id]
  if (max_fpr <= min(x)) {
    return(0)
  }
  if (max_fpr < max(x)) {
    y_max <- stats::approx(x, y, xout = max_fpr, ties = "ordered")$y
    keep <- x < max_fpr
    x <- c(x[keep], max_fpr)
    y <- c(y[keep], y_max)
  } else {
    keep <- x <= max_fpr
    x <- x[keep]
    y <- y[keep]
  }
  if (length(x) < 2) {
    return(0)
  }
  sum(diff(x) * zoo::rollmean(y, 2))
}

for (smaller_size in smaller_size.choice){
  for (i.model in c(1:n.model)){
    df.temp <- nproc.test.df[which(nproc.test.df$screen.size == smaller_size),]
    x <- df.temp$missed.crises
    y <- df.temp[,i.model+2]
    id <- order(x)
    df.auc.test[i.model,which(smaller_size.choice==smaller_size)] <- sum(diff(x[id])*zoo::rollmean(y[id],2))
    df.pauc.test[i.model,which(smaller_size.choice==smaller_size)] <- pauc_np(x, y, max_fpr = pauc.max.fpr)
  }
}
df.auc.test$model <- model.choice
df.auc.test <- df.auc.test[, c("model", feature_cols)]
write.csv(df.auc.test, "./outputs/AUC_test_90 CI.csv", row.names = FALSE)

df.pauc.test$model <- model.choice
df.pauc.test <- df.pauc.test[, c("model", feature_cols)]
write.csv(df.pauc.test, "./outputs/pAUC_test_90_CI_FPR_le_0.25.csv", row.names = FALSE)

```

### ROC curves (standard) and AUC table
```{r roc_standard}
roc.alpha <- 0.9
roc.delta <- 0.1
roc.plot.size <- max(smaller_size.choice)

roc_curve_rds <- rds_path("roc_curve_df.rds")
roc_auc_rds <- rds_path("roc_auc_table.rds")
use_cached_roc <- use_cached_rds &&
  file.exists(roc_curve_rds) &&
  file.exists(roc_auc_rds)

if (use_cached_roc) {
  roc_curve_df <- readRDS(roc_curve_rds)
  roc_auc_table <- readRDS(roc_auc_rds)
} else {
  if (is.null(screen.rank)) {
    if (method_screening == "Goffins"){
      data_screening <- list("x" = trainingSample.NP[, predictor.name], "y" = trainingSample.NP$outcome)
      screen.rank <- getGFsize(data_screening, family.type = 1)$rank
    }else if(method_screening == "Kfilter"){
      screen.rank <- k.filter(x = trainingSample.NP[, predictor.name], y =as.factor(trainingSample.NP$outcome), response.type = "categorical")$k.rank
    }else if(method_screening == "SIRS"){
      screen.rank <- SIRS(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
    }else if (method_screening == "DC"){
      screen.rank <- DC(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
    }else{
      stop(paste("Unknown method_screening:", method_screening))
    }
  }

  roc_auc_table <- data.frame(model = model.choice,
                              matrix(NA_real_, nrow = n.model, ncol = length(smaller_size.choice)))
  colnames(roc_auc_table)[-1] <- feature_cols

  roc_curve_list <- list()

  for (smaller_size in smaller_size.choice){
    predictor.name.smaller <- predictor.name[which(screen.rank <= smaller_size)]

    for (i.model in seq_len(n.model)){
      if (i.model == 1){
        model.trained <- npc.signalextraction(trainingSample.NP, trainingSample.NP$outcome, predictor.name.smaller,
                                              alpha = roc.alpha, delta = roc.delta, split = 1, split.ratio = 0.5,
                                              n.cores = 1, randseed = 0)
        score.test <- 1 - predict.signalextraction(testSample.NP, model.trained, predictor.name.smaller)
      }else{
        model.trained <- nproc::npc(trainingSample.NP[, predictor.name.smaller], trainingSample.NP$outcome,
                             method = model.choice[i.model], alpha = roc.alpha, delta = roc.delta,
                             split = 1, split.ratio = 0.5, n.cores = 1, randSeed = 0)
        pred.test <- predict(model.trained, testSample.NP[, predictor.name.smaller])
        score.test <- 1 - pred.test$pred.score
      }

      scores <- as.numeric(score.test)
      labels <- as.numeric(testSample$outcome)

      pred <- ROCR::prediction(scores, labels)
      auc.val <- as.numeric(ROCR::performance(pred, "auc")@y.values[[1]])
      roc_auc_table[i.model, which(smaller_size.choice == smaller_size) + 1] <- auc.val

      if (smaller_size == roc.plot.size) {
        perf <- ROCR::performance(pred, "tpr", "fpr")
        roc_curve_list[[length(roc_curve_list) + 1]] <- data.frame(
          fpr = perf@x.values[[1]],
          tpr = perf@y.values[[1]],
          Model = model.choice[i.model]
        )
      }
    }
  }

  write.csv(roc_auc_table, "./outputs/ROC_AUC_test_90 CI.csv", row.names = FALSE)

  roc_curve_df <- do.call(rbind, roc_curve_list)
  save_rds(roc_curve_df, "roc_curve_df.rds")
  save_rds(roc_auc_table, "roc_auc_table.rds")
}
# Ensure the CSV exists even when using cached .rds files.
write.csv(roc_auc_table, "./outputs/ROC_AUC_test_90 CI.csv", row.names = FALSE)
# roc_curve_df$Model <- factor(roc_curve_df$Model, levels = model.choice)

# plot.roc.standard <- ggplot(data = roc_curve_df) +
#   geom_line(aes(x = fpr, y = tpr, color = Model), size = 1) +
#   labs(x = "False Positive Rate", y = "True Positive Rate") +
#   xlim(0,1) +
#   ylim(0,1) +
#   theme(panel.background = element_rect(fill = "white"),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.border = element_rect(color = "grey50", fill = NA),
#         legend.position = "top",
#         legend.key = element_rect(colour = "transparent", fill = "white"),
#         axis.text = element_text(size = 12),
#         axis.title = element_text(size = 12),
#         legend.text = element_text(size = 12),
#         legend.title = element_text(size = 12)) +
#   geom_abline(intercept = 0, slope = 1, linetype = "dashed")

# plot.roc.standard
# ggsave(paste0("./outputs/roc_standard_test_models_features_", roc.plot.size, ".png"),
#        plot = plot.roc.standard, width = 6, height = 6)
```

### Backtesting Performance of Models (Tables)

```{r backtesting_performance_tables, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
as_paper_backtesting_table <- function(df) {
  df <- as.data.frame(df, stringsAsFactors = FALSE)
  if (!"model" %in% names(df)) stop("Expected a column named 'model'.", call. = FALSE)

  desired <- paste0("features_", c(10, 20, 30, 40, 50, 60))
  desired <- desired[desired %in% names(df)]
  all_col <- if ("features_71" %in% names(df)) "features_71" else if ("features_70" %in% names(df)) "features_70" else NA_character_
  if (is.na(all_col)) {
    feat_cols <- grep("^features_\\d+$", names(df), value = TRUE)
    if (length(feat_cols) > 0) all_col <- tail(feat_cols, 1)
  }
  cols <- c("model", desired, all_col)
  cols <- cols[!is.na(cols) & cols %in% names(df)]

  out <- df[, cols, drop = FALSE]

  model_labels <- c(
    "SE" = "Signal-Extraction",
    "logistic" = "Logistic",
    "svm" = "SVM",
    "randomforest" = "Random Forests",
    "ada" = "AdaBoost"
  )

  out$model <- ifelse(out$model %in% names(model_labels), model_labels[out$model], out$model)
  out$model <- factor(out$model, levels = unname(model_labels))
  out <- out[order(out$model), , drop = FALSE]
  out$model <- as.character(out$model)

  for (nm in names(out)) {
    if (nm == "model") next
    if (is.character(out[[nm]])) out[[nm]] <- suppressWarnings(as.numeric(out[[nm]]))
  }

  if (ncol(out) >= 2) {
    num_cols <- setdiff(names(out), "model")
    out[num_cols] <- lapply(out[num_cols], function(x) round(x, 3))
  }

  col_labels <- c(
    "model" = "Model",
    "features_10" = "$d=10$",
    "features_20" = "$d=20$",
    "features_30" = "$d=30$",
    "features_40" = "$d=40$",
    "features_50" = "$d=50$",
    "features_60" = "$d=60$"
  )
  if (!is.na(all_col) && all_col %in% names(out)) {
    col_labels[all_col] <- "All"
  }
  colnames(out) <- ifelse(names(out) %in% names(col_labels), col_labels[names(out)], names(out))

  out
}

render_kable <- function(tbl, caption) {
  cat(knitr::kable(tbl, format = "html", caption = caption, align = "c"), sep = "\n")
  cat("\n\n")
}

render_kable(
  as_paper_backtesting_table(df.auc.test),
  "Area Under the NP-ROC Curve (AUC)"
)
render_kable(
  as_paper_backtesting_table(df.pauc.test),
  "Area Under the Partial NP-ROC Curve (AUPC)"
)
render_kable(
  as_paper_backtesting_table(roc_auc_table),
  "Area Under the Standard ROC Curve (AUC)"
)

cat(
  "<p><em>Notes.</em> For NP-ROC AUC and AUPC, the violation rate of the model estimation under the NP classification paradigm is set to be ",
  "$\\delta = 0.1$, which implies the percentage of missed crises is maintained under different upper bounds with a probability of at least 90\\%. ",
  "Columns two through seven correspond to model performance with feature screening: $d=i$ where $i=10,20,30,40,50,60$ indicates the number of features used in the model estimation, ",
  "and the last column shows model performance with the full feature set. Standard ROC AUC is computed on the same test sample.</p>\n",
  sep = ""
)
```



```{r}
# (optional) if you need to harmonize legend labels like your other plot
roc_curve_df$Model[roc_curve_df$Model == "SE"] <- "Signal-Extraction"
roc_curve_df$Model[roc_curve_df$Model == "ada"] <- "AdaBoost"
roc_curve_df$Model[roc_curve_df$Model == "logistic"] <- "Logistic"
roc_curve_df$Model[roc_curve_df$Model == "svm"] <- "SVM"
roc_curve_df$Model[roc_curve_df$Model == "randomforest"] <- "Random Forests"

roc_curve_df$Model <- factor(
  roc_curve_df$Model,
  levels = c("Signal-Extraction", "Logistic", "SVM", "Random Forests", "AdaBoost")
)

save_rds(roc_curve_df, "roc_curve_df.rds")
save_rds(roc_auc_table, "roc_auc_table.rds")

plot.roc.standard <- ggplot(data = roc_curve_df) +
  geom_line(aes(x = fpr, y = tpr, color = Model, linetype = Model), size = 1) +
  labs(x = "Type II error", y = "1 - conditional type I error", color = NULL, linetype = NULL) +
  xlim(0, 1) +
  ylim(0, 1) +
  scale_linetype_manual(values = c("solid", "dashed", "dotdash", "twodash", "longdash")) +
  theme(
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "grey50", fill = NA),
    legend.position = "top",
    legend.key = element_rect(colour = "transparent", fill = "white"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  ) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))

#plot.roc.standard

#ggsave(paste0("./outputs/roc_standard_test_models_features_", #roc.plot.size, ".png"),plot = plot.roc.standard, width = 6, height = 6)
```

```{r best model}
row.id <- 0

nproc.tranining.best <- list()
nproc.test.best <- list()

nproc_train_rds <- rds_path("nproc_training_long.rds")
nproc_test_rds <- rds_path("nproc_test_long.rds")
use_cached_nproc <- use_cached_rds &&
  file.exists(nproc_train_rds) &&
  file.exists(nproc_test_rds)

smaller_size.choice <- 71

if (!use_cached_nproc) {
screen.rank <- NULL
if (method_screening == "Goffins"){
  data_screening <- list("x" = trainingSample.NP[, predictor.name], "y" = trainingSample.NP$outcome)
  screen.rank <- getGFsize(data_screening, family.type = 1)$rank
}else if(method_screening == "Kfilter"){
  screen.rank <- k.filter(x = trainingSample.NP[, predictor.name], y =as.factor(trainingSample.NP$outcome), response.type = "categorical")$k.rank
  write.csv(screen.rank, "./outputs/Rank_Kfilter.csv")
}else if(method_screening == "SIRS"){
  screen.rank <- SIRS(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
}else if (method_screening == "DC"){
  screen.rank <- DC(X = trainingSample.NP[, predictor.name],Y = trainingSample.NP$outcome)$rank
}else{
  stop(paste("Unknown method_screening:", method_screening))
}

combo.best <- expand.grid(smaller_size = smaller_size.choice, alpha = alpha.choice, KEEP.OUT.ATTRS = FALSE, stringsAsFactors = FALSE)

n_cores_requested <- 12L
n_cores_available <- parallel::detectCores(logical = FALSE)
if (is.na(n_cores_available)) {
  n_cores_available <- parallel::detectCores(logical = TRUE)
}
n_cores <- min(n_cores_requested, n_cores_available, nrow(combo.best))
if (is.na(n_cores) || n_cores < 1L) {
  n_cores <- 1L
}

cl <- parallel::makeCluster(n_cores)
doParallel::registerDoParallel(cl)

nproc.best.results <- foreach(row_idx = seq_len(nrow(combo.best)),
                              .combine = rbind,
                              .packages = c("nproc", "e1071", "randomGLM", "ROSE", "rpart"),
                              .export = c("npc.signalextraction", "npc.signalextraction.split", "npc_aux.core",
                                          "predict.signalextraction", "SumErrors.label")) %dopar% {
  alpha <- combo.best$alpha[row_idx]
  smaller_size <- combo.best$smaller_size[row_idx]

  predictor.name.smaller <- predictor.name[which(screen.rank <= smaller_size)]

  train_vals <- setNames(rep(NA_real_, n.model), model.choice)
  test_vals <- setNames(rep(NA_real_, n.model), model.choice)

  for (i.model in seq_len(n.model)){

    Performance$Data[res.id] <- Datasets[data]
    Performance$year.cutoff[res.id] <- year.cutoff
    Performance$Model[res.id] <- model.choice[i.model]

    print(c(Datasets[data], year.cutoff, model.choice[i.model]))

    ##### "Neyman-Pearson::Signal Extraction Model" #####

    if (i.model == 1){
      model.trained <- npc.signalextraction(trainingSample.NP, trainingSample.NP$outcome, predictor.name.smaller, alpha = alpha, delta = 0.2, split = 1, split.ratio = 0.5, n.cores = 1, randseed = 0)
      score.training <- 1-predict.signalextraction(trainingSample.NP, model.trained, predictor.name.smaller)
      score.test <- 1-predict.signalextraction(testSample.NP, model.trained, predictor.name.smaller)
      label.training <- ifelse(score.training > 0.5, 1, 0)
      label.test <- ifelse(score.test > 0.5, 1, 0)
    }else{
      model.trained <- nproc::npc(trainingSample.NP[, predictor.name.smaller], trainingSample.NP$outcome, method = model.choice[i.model], alpha = alpha, delta = 0.2, split = 1, split.ratio = 0.5, n.cores = 1, randSeed = 0)
      pred.training <- predict(model.trained, trainingSample.NP[, predictor.name.smaller])
      pred.test <- predict(model.trained, testSample.NP[, predictor.name.smaller])
      score.training <- 1 - pred.training$pred.score
      score.test <- 1 - pred.test$pred.score
      label.training <- 1 - pred.training$pred.label
      label.test <- 1 - pred.test$pred.label
    }

    names(score.training) <- "Score"
    names(score.test) <- "Score"

    posterior.training <- cbind(trainingSample[,c("Country_Code", "Country_Name", "Year", "SuddenStop_GI")], score.training)
    posterior.test <- cbind(testSample[,c("Country_Code", "Country_Name", "Year", "SuddenStop_GI")], score.test)

    print("test")

    train_vals[[model.choice[i.model]]] <- ifelse(is.na(SumErrors.label(label.training, trainingSample$outcome, weight = NULL)$false), 0, 1-SumErrors.label(label.training, trainingSample$outcome, weight = NULL)$false)
    test_vals[[model.choice[i.model]]] <- ifelse(is.na(SumErrors.label(label.test, testSample$outcome, weight = NULL)$false), 0, 1-SumErrors.label(label.test, testSample$outcome, weight = NULL)$false)

  }

  c(
    missed.crises = alpha,
    screen.size = smaller_size,
    setNames(train_vals, paste0("train_", model.choice)),
    setNames(test_vals, paste0("test_", model.choice))
  )
}

parallel::stopCluster(cl)

nproc.best.results <- as.data.frame(nproc.best.results, stringsAsFactors = FALSE)
nproc.tranining.df.best <- nproc.best.results[, c("missed.crises", "screen.size", paste0("train_", model.choice))]
names(nproc.tranining.df.best) <- c("missed.crises", "screen.size", model.choice)

nproc.test.df.best <- nproc.best.results[, c("missed.crises", "screen.size", paste0("test_", model.choice))]
names(nproc.test.df.best) <- c("missed.crises", "screen.size", model.choice)
}
```
### ROC plot - training
```{r}
if (use_cached_nproc) {
  nproc.training.long <- readRDS(nproc_train_rds)
} else {
  nproc.tranining.df.best$V1 <- NULL
  nproc.tranining.df.best$screen.size <- NULL
  nproc.training.long <- nproc.tranining.df.best %>%
    tidyr::pivot_longer(!missed.crises, names_to = "label", values_to = "value")

  save_rds(nproc.training.long, "nproc_training_long.rds")
}

plot.nproc.training <- ggplot(data = nproc.training.long) +
  geom_line(aes(x = missed.crises, y = value, color = label, linetype = label), size = 1) + 
  labs(y = "1-conditional type II error",  x = "Type I error bound", color = NULL, linetype = NULL) + 
  # guides(linetype = guide_legend(title = "Type II error band")) + 
  # scale_linetype_manual(labels = c("lower bound", "upper bound"), values = c(1,3)) + 
  scale_linetype_manual(values = c("solid", "dashed", "dotdash", "twodash", "longdash")) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "grey50", fill = NA)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed")


#plot.nproc.training
#ggsave("./outputs/roc_training_nproc_models.png", plot = plot.nproc.training, width = 6, height = 6)

```

### ROC plot - test
```{r roc}
if (use_cached_nproc) {
  nproc.test.long <- readRDS(nproc_test_rds)
} else {
  nproc.test.df.best$V1 <- NULL
  nproc.test.df.best$screen.size <- NULL
  nproc.test.long <- nproc.test.df.best %>%
    tidyr::pivot_longer(!missed.crises, names_to = "label", values_to = "value")

  nproc.test.long$label[which(nproc.test.long$label == "SE")] <- "Signal-Extraction"
  nproc.test.long$label[which(nproc.test.long$label == "ada")] <- "AdaBoost"
  nproc.test.long$label[which(nproc.test.long$label == "logistic")] <- "Logistic"
  nproc.test.long$label[which(nproc.test.long$label == "svm")] <- "SVM"
  nproc.test.long$label[which(nproc.test.long$label == "randomforest")] <- "Random Forests"

  colnames(nproc.test.long)[2] <- "Model"

  nproc.test.long$Model <- factor(nproc.test.long$Model, levels = c("Signal-Extraction", "Logistic", "SVM", "Random Forests", "AdaBoost"))

  write.csv(nproc.test.long, "./outputs/Data_for_AUC_90_CI.csv")
  save_rds(nproc.test.long, "nproc_test_long.rds")
}

plot.nproc.test <- ggplot(data = nproc.test.long) +
  geom_line(aes(x = missed.crises, y = value, color = Model, linetype = Model), size = 1) + 
  labs(y = "1 - conditional type I error",  x = "Type II error bound", color = NULL, linetype = NULL) + 
  xlim(0,1) + 
  ylim(0,1) +
  scale_linetype_manual(values = c("solid", "dashed", "dotdash", "twodash", "longdash")) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "grey50", fill = NA),
        legend.position = "top",
        legend.key = element_rect(colour = "transparent", fill = "white"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12))+
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  annotate("rect", xmin = 0, xmax = 0.25, ymin = 0, ymax = 1, alpha = .2) +
  guides(color=guide_legend(nrow=2,byrow=TRUE))


plot.nproc.test
```


### Combine
```{r}
#plot.combine <- ggarrange(plot.nproc.training, plot.nproc.test,common.legend = TRUE, legend = "top", ncol = 2, labels = c("training", "test"))
#plot.combine
#ggsave("./outputs/roc_training_test_nproc_models.png", plot = plot.combine, width = 10, height = 5)
```


### Combine
```{r}
plot.combine <- ggpubr::ggarrange(plot.roc.standard, plot.nproc.test,common.legend = TRUE, legend = "top", ncol = 2, labels = c("Classic ROC", "NP-ROC"),
  label.x = 0.5,     # center horizontally
  label.y = 1,       # top of panel
  hjust = 0.5,       # center text horizontally
  vjust = 2)        # move label slightly down into panel)
plot.combine
ggsave("./outputs/roc_classic_nproc_models.png", plot = plot.combine, width = 10, height = 5)
```


### Calibration (np-crisis.R)
```{r np-crisis calibration}
delta_0 <- 0.1  # violation probability in the NP classification
External_database_cal <- "External_database"
Crisis_definition_cal <- "_withSuddenStopGI"
Period_coverage_cal <- "_19802019"
Date_constructed_cal <- "_public_08_04_2019"
year.cutoff_choice <- seq(1990, 2016, 1)
forecasting_horizon_cal <- 1
if (forecasting_horizon_cal == 1){
  suffix_cal <- "_forecasting_h1_v12"
}
test.size <- 1
model.choice_cal <- c("SE", "logistic", "svm", "randomforest", "ada")
i.model <- 1 # 1: SE, 2: logistic, 3: svm, 4: randomforest, 5: ada

filename_cal <- file.path(
  data_dir,
  paste0(External_database_cal, Crisis_definition_cal, Period_coverage_cal, Date_constructed_cal, suffix_cal, ".dta")
)
Crisis_Data <- foreign::read.dta(file.path(data_dir, "Calibration_CrisisIdentificationData_53EM_19802017_10_29_2018.dta"), missing.type = FALSE, convert.underscore = FALSE)
GlobalShocks_Data <- foreign::read.dta(file.path(data_dir, "Calibration_GlobalShocksData_19802017.dta"), missing.type = FALSE, convert.underscore = FALSE)
current_calibration <- foreign::read.dta(filename_cal, missing.type = FALSE, convert.underscore = FALSE)
current_calibration$outcome <- current_calibration$SuddenStop_GI
firstvar <- 5

Country_Crisis <- aggregate(current_calibration[current_calibration$Year <= 2003,]$SuddenStop_GI, by=list(Category = current_calibration[current_calibration$Year <= 2003,]$Country_Name), FUN = sum, na.rm = TRUE)
names(Country_Crisis) <- c('Country.Name', 'Num.Crisis')
Country.list <- Country_Crisis$Country.Name
Country.list[length(Country.list)+1] <- "Aggregate"

calibration_id <- 0
CrossSectional_Calibration <- data.frame(matrix(, nrow = length(Country.list)*length(year.cutoff_choice), ncol = 9))
names(CrossSectional_Calibration) <- c("Country.Name", "Year.cutoff", "lambda", "pi.mean", "gamma_all", "gamma_outputfall", "gamma", "g", "delta")
for (country in Country.list){
  for (year.cutoff in year.cutoff_choice){
    calibration_id <- calibration_id + 1
    CrossSectional_Calibration$Country.Name[calibration_id] <- country
    CrossSectional_Calibration$Year.cutoff[calibration_id] <- year.cutoff
    if (country == "Aggregate"){
      lambda <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_capflp_pch_gdp"], na.rm = TRUE)*(-1)/100
    }else{
      lambda <- mean(Crisis_Data[Crisis_Data$Country_Name == country & Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_capflp_pch_gdp"], na.rm = TRUE)*(-1)/100
    }
    if (is.nan(lambda)){
      lambda <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_capflp_pch_gdp"], na.rm = TRUE)*(-1)/100
    }
    CrossSectional_Calibration$lambda[calibration_id] <- lambda
    if (country == "Aggregate"){
      pi.mean <- mean(Crisis_Data[Crisis_Data$Year < year.cutoff, "Crisis_GI_Adjusted"])
    }else{
      pi.mean <- mean(Crisis_Data[Crisis_Data$Country_Name == country & Crisis_Data$Year < year.cutoff, "Crisis_GI_Adjusted"])
    }
    if (is.na(pi.mean) || pi.mean == 0){
      pi.mean <- mean(Crisis_Data[Crisis_Data$Year < year.cutoff, "Crisis_GI_Adjusted"])
    }
    CrossSectional_Calibration$pi.mean[calibration_id] <- pi.mean
    if (country == "Aggregate"){
      gamma_all <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_RGDP_Growth"], na.rm = TRUE)
    }else{
      gamma_all <- mean(Crisis_Data[Crisis_Data$Country_Name == country & Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_RGDP_Growth"], na.rm = TRUE)
    }
    if (is.nan(gamma_all)){
      gamma_all <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1, "d_RGDP_Growth"], na.rm = TRUE)
    }
    CrossSectional_Calibration$gamma_all[calibration_id] <- gamma_all
    if (country == "Aggregate"){
      gamma_outputfall <-  median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1 & Crisis_Data$d_RGDP_Growth < 0, "d_RGDP_Growth"], na.rm = TRUE)
    }else{
      gamma_outputfall <-  mean(Crisis_Data[Crisis_Data$Country_Name == country & Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1 & Crisis_Data$d_RGDP_Growth < 0, "d_RGDP_Growth"], na.rm = TRUE)
    }
    if (is.nan(gamma_outputfall)){
      gamma_outputfall <-  median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 1 & Crisis_Data$d_RGDP_Growth < 0, "d_RGDP_Growth"], na.rm = TRUE)
    }
    CrossSectional_Calibration$gamma_outputfall[calibration_id] <- gamma_outputfall
    gamma = 1/2*(gamma_outputfall + gamma_outputfall)*(-1)/100
    CrossSectional_Calibration$gamma[calibration_id] <- gamma
    if (country == "Aggregate"){
      g <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 0, "RGDP_Growth"], na.rm = TRUE)/100
    }else{
      g <- mean(Crisis_Data[Crisis_Data$Country_Name == country & Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 0, "RGDP_Growth"], na.rm = TRUE)/100
    }
    if (is.nan(g)){
      g <- median(Crisis_Data[Crisis_Data$Year < year.cutoff & Crisis_Data$Crisis_GI_Adjusted == 0, "RGDP_Growth"], na.rm = TRUE)/100
    }
    CrossSectional_Calibration$g[calibration_id] <- g
    delta <- median(GlobalShocks_Data[GlobalShocks_Data$Year < year.cutoff, "risk_premium"])/100
    CrossSectional_Calibration$delta[calibration_id] <- delta
  }
}
readr::write_csv(CrossSectional_Calibration, file = file.path(output_dir, "CrossSectional_Calibration_NP.csv"))
```

### Alpha calibration (np-crisis.R)
```{r np-crisis alpha calibration}
crosssectional_calibration <- 1
alpha_mse_rds <- rds_path("alpha_calibration_mse_by_year.rds")
alpha_min_rds <- rds_path("alpha_calibration_min_mse_by_year.rds")
use_cached_alpha_cal <- use_cached_rds &&
  file.exists(alpha_mse_rds) &&
  file.exists(alpha_min_rds)
if(crosssectional_calibration == 1){
  Country.list <- c("Aggregate")
  alpha.choice_cal <- seq(from = 0.1, to = 1, by = 0.05)
  if (use_cached_alpha_cal) {
    Annually_Calibrated_Alpha_mse <- readRDS(alpha_mse_rds)
    Annually_Calibrated_Alpha <- readRDS(alpha_min_rds)
  } else {
    mse.alpha <- reserves_match.mse.alpha(alpha.choice_cal, current_calibration, year.cutoff_choice, test.size, Country.list, CrossSectional_Calibration, model.choice_cal, i.model,delta = delta_0)
    DT.mse.alpha <- data.table::data.table(mse.alpha)
    Annually_Calibrated_Alpha_mse <- mse.alpha %>%
      group_by(Year.cutoff, Alpha) %>%
      summarise(mse = mean((Reserves.optimal - Reserves.observed)^2, na.rm = TRUE))
    DT.mse <- data.table::data.table(Annually_Calibrated_Alpha_mse)
    Annually_Calibrated_Alpha_mse_min <- DT.mse[ , .SD[which.min(mse)], by = "Year.cutoff"]
    save_rds(Annually_Calibrated_Alpha_mse, "alpha_calibration_mse_by_year.rds")
    DT.mse.alpha <- data.table::data.table(mse.alpha)
    mse.alpha$Reserves.error.squared <- mse.alpha$Reserves.error^2
    Annually_Calibrated_Alpha <- DT.mse.alpha[ , .SD[which.min(Reserves.error.squared)], by = c("Country.Name", "Year.cutoff")]
    save_rds(Annually_Calibrated_Alpha, "alpha_calibration_min_mse_by_year.rds")
    mse.alpha$Reserves.error_square <- mse.alpha$Reserves.error^2
    TimeInvariant_Calibrated_Alpha <- aggregate(mse.alpha$Reserves.error_square, by=list(Category = mse.alpha$Alpha), FUN = mean, na.rm = TRUE)
    names(TimeInvariant_Calibrated_Alpha) <- c("Alpha", "MSE")
    readr::write_csv(TimeInvariant_Calibrated_Alpha, file = file.path(output_dir, "TimeInvariant_Calibrated_Alpha_NP.csv"))
  }
  #plot.alpha.mse <- ggplot(Annually_Calibrated_Alpha_mse, aes(x=Year.cutoff, y=Alpha)) + geom_point()
  #plot.alpha.mse
  #ggsave("./outputs/alpha_calibration_mse_by_year.png", plot = plot.alpha.mse, width = 7, height = 4)
  #plot.alpha.annual <- ggplot(Annually_Calibrated_Alpha, aes(x=Year.cutoff, y=Alpha)) + geom_point()
  #plot.alpha.annual
  #ggsave("./outputs/alpha_calibration_min_mse_by_year.png", plot = plot.alpha.annual, width = 7, height = 4)
}
```

### Visualizing the results (np-crisis.R)
```{r np-crisis visualization}
data_plot_rds <- rds_path("alpha_calibration_smoothed_data.rds")
use_cached_alpha_plot <- use_cached_rds && file.exists(data_plot_rds)

if (use_cached_alpha_plot) {
  data.plot <- readRDS(data_plot_rds)
} else {
  data.crisis_freq <- current_calibration %>%
    group_by(Year) %>%
    summarise(Crisis.Freq = sum(SuddenStop_GI, na.rm = TRUE))
  data.crisis_freq$Year <- data.crisis_freq$Year - 2
  data.plot <- merge(Annually_Calibrated_Alpha[,c("Year.cutoff", "Alpha")], data.crisis_freq, by.x = "Year.cutoff", by.y = "Year", all.x = TRUE)
  data.plot$Year.cutoff <- data.plot$Year.cutoff + 2

  fit <- loess(data.plot$Alpha ~ data.plot$Year.cutoff, span = 0.3)
  data.plot$Alpha_smoothed <- predict(fit)
  save_rds(data.plot, "alpha_calibration_smoothed_data.rds")
}

myplot <- ggplot(data = data.plot %>% filter(Year.cutoff <= 2017), aes(x = Year.cutoff)) +
  geom_bar(aes(y = Crisis.Freq/max(Crisis.Freq)), stat = "identity", alpha = 0.5) +
  geom_line(aes(y = Alpha_smoothed), size = 1, color = "grey30") +
  scale_y_continuous(
    name = "Alpha (smoothed)",
    sec.axis = sec_axis(~., name = "Normalized Crisis Frequency")
  ) + scale_x_continuous(breaks = seq(1982, 2016, 2),
                         name = "Year")
#ggsave("./outputs/alpha_crisis_calibration_smoothed.pdf", plot = myplot, width = 8, height = 5)
```

### Bootstrap confidence bands for alpha (additional analysis)
```{r np-crisis alpha bootstrap}
set.seed(123)
alpha_ci_rds <- rds_path("alpha_calibration_bootstrap_ci.rds")
data_plot_ci_rds <- rds_path("alpha_calibration_bootstrap_data_plot.rds")
use_cached_boot <- use_cached_rds &&
  file.exists(alpha_ci_rds) &&
  file.exists(data_plot_ci_rds)

if (use_cached_boot) {
  alpha_ci <- readRDS(alpha_ci_rds)
  data.plot.ci <- readRDS(data_plot_ci_rds)
} else {
  #bootstrap_reps <- 500 #took about 4 hours to run on a 12-core machine
  bootstrap_reps <- 500 
  bootstrap_level <- 0.90
  bootstrap_use_parallel <- TRUE
  bootstrap_workers <- max(1, parallel::detectCores() - 2)

  country_boot_pool <- sort(unique(current_calibration$Country_Name))
  country_boot_pool <- country_boot_pool[!is.na(country_boot_pool)]

  bootstrap_alpha <- NULL

  if (bootstrap_use_parallel) {
    cl <- parallel::makeCluster(bootstrap_workers)
    on.exit(parallel::stopCluster(cl), add = TRUE)
    doParallel::registerDoParallel(cl)
    parallel::clusterSetRNGStream(cl, 123)
    parallel::clusterEvalQ(cl, { source("np-crisis-helper-funcs.R") })
    parallel::clusterExport(
      cl,
      varlist = c(
        "current_calibration", "country_boot_pool", "alpha.choice_cal",
        "year.cutoff_choice", "test.size", "Country.list", "firstvar",
        "CrossSectional_Calibration", "model.choice_cal",
        "i.model", "delta_0", "reserves_match.mse.alpha"
      ),
      envir = environment()
    )

    bootstrap_alpha <- tryCatch(
      foreach::foreach(
        b = seq_len(bootstrap_reps),
        .packages = c("dplyr", "nproc")
      ) %dopar% {
        boot_countries <- sample(country_boot_pool, size = length(country_boot_pool), replace = TRUE)
        boot_list <- lapply(boot_countries, function(cty) current_calibration[current_calibration$Country_Name == cty, ])
        current_boot <- bind_rows(boot_list)
        current_boot$outcome <- current_boot$SuddenStop_GI

        mse.alpha.boot <- reserves_match.mse.alpha(
          alpha.choice_cal, current_boot, year.cutoff_choice, test.size,
          Country.list, CrossSectional_Calibration, model.choice_cal, i.model, delta = delta_0
        )
        mse.alpha.boot$Reserves.error.squared <- mse.alpha.boot$Reserves.error^2
        DT.mse.alpha.boot <- data.table::data.table(mse.alpha.boot)
        annually_alpha_boot <- DT.mse.alpha.boot[ , .SD[which.min(Reserves.error.squared)], by = c("Country.Name", "Year.cutoff")]

        annually_alpha_boot %>%
          select(Year.cutoff, Alpha) %>%
          mutate(rep = b)
      },
      error = function(e) {
        message("Parallel bootstrap failed; falling back to sequential. Error: ", conditionMessage(e))
        NULL
      }
    )
  }

  if (is.null(bootstrap_alpha)) {
    bootstrap_alpha <- vector("list", bootstrap_reps)
    for (b in seq_len(bootstrap_reps)) {
      cat("Bootstrap replication:", b, "\n")
      boot_countries <- sample(country_boot_pool, size = length(country_boot_pool), replace = TRUE)
      boot_list <- lapply(boot_countries, function(cty) current_calibration[current_calibration$Country_Name == cty, ])
      current_boot <- bind_rows(boot_list)
      current_boot$outcome <- current_boot$SuddenStop_GI

      mse.alpha.boot <- reserves_match.mse.alpha(
        alpha.choice_cal, current_boot, year.cutoff_choice, test.size,
        Country.list, CrossSectional_Calibration, model.choice_cal, i.model, delta = delta_0
      )
      mse.alpha.boot$Reserves.error.squared <- mse.alpha.boot$Reserves.error^2
      DT.mse.alpha.boot <- data.table::data.table(mse.alpha.boot)
      annually_alpha_boot <- DT.mse.alpha.boot[ , .SD[which.min(Reserves.error.squared)], by = c("Country.Name", "Year.cutoff")]

      bootstrap_alpha[[b]] <- annually_alpha_boot %>%
        select(Year.cutoff, Alpha) %>%
        mutate(rep = b)
    }
  }

  bootstrap_alpha_df <- bind_rows(bootstrap_alpha)

  #change to compute the standard errors +- visualization
  alpha_ci <- bootstrap_alpha_df %>%
    group_by(Year.cutoff) %>%
    summarise(
      Alpha_low = quantile(Alpha, probs = (1 - bootstrap_level) / 2, na.rm = TRUE),
      Alpha_high = quantile(Alpha, probs = 1 - (1 - bootstrap_level) / 2, na.rm = TRUE),
      Alpha_se = sd(Alpha, na.rm = TRUE)
    )

  alpha_ci$Year.cutoff <- alpha_ci$Year.cutoff + 2

  data.plot.ci <- data.plot %>%
    left_join(alpha_ci, by = "Year.cutoff")

  save_rds(alpha_ci, "alpha_calibration_bootstrap_ci.rds")
  save_rds(data.plot.ci, "alpha_calibration_bootstrap_data_plot.rds")
}

readr::write_csv(alpha_ci, "./outputs/alpha_calibration_bootstrap_ci.csv")

myplot_ci <- ggplot(data = data.plot.ci %>% filter(Year.cutoff <= 2017), aes(x = Year.cutoff)) +
  geom_bar(aes(y = Crisis.Freq/max(Crisis.Freq)), stat = "identity", alpha = 0.5) +
  geom_ribbon(aes(ymin = pmax(0,Alpha - 1 * Alpha_se), ymax = pmin(1, Alpha + 1 * Alpha_se)), fill = "grey70", alpha = 0.4) +
  geom_line(aes(y = Alpha), size = 1, color = "grey30") +
  scale_y_continuous(
    name = "Alpha",
    sec.axis = sec_axis(~., name = "Normalized Crisis Frequency")
  ) + scale_x_continuous(breaks = seq(1982, 2016, 2),
                         name = "Year")
myplot_ci
ggsave("./outputs/alpha_crisis_calibration_1sd.pdf", plot = myplot_ci, width = 8, height = 5)

# myplot_ci <- ggplot(data = data.plot.ci %>% filter(Year.cutoff <= 2017), aes(x = Year.cutoff)) +
#   geom_bar(aes(y = Crisis.Freq/max(Crisis.Freq)), stat = "identity", alpha = 0.5) +
#   geom_ribbon(aes(ymin = Alpha_low, ymax = Alpha_high), fill = "dodgerblue2", alpha = 0.2) +
#   geom_line(aes(y = Alpha_smoothed), size = 1, color = "dodgerblue2") +
#   scale_y_continuous(
#     name = "Alpha (smoothed)",
#     sec.axis = sec_axis(~., name = "Normalized Crisis Frequency")
#   ) + scale_x_continuous(breaks = seq(1982, 2016, 2),
#                          name = "Year")

# ggsave("./outputs/alpha_crisis_calibration_smoothed_ci.pdf", plot = myplot_ci, width = 8, height = 5)
```
